Eco-evolutionary dynamics of finite populations from first principles

### 2023-03-15 ind_files/05_unification_discussion.tex
Change epigraph to Brenner quote

\epigraph{\justifying The grand aim of all science [is] to cover the greatest number of empirical facts by logical deduction from the smallest number of hypotheses or axioms}{Albert Einstein~\citep{barnett_universe_1952}}

>>>>

\epigraph{\justifying Writing in the last months of this millenium, it is clear that the prime intellectual task of the future lies in constructing an appropriate theoretical framework for biology}{Sydney Brenner~\citep{brenner_theoretical_1999}}
